Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-15 surfaces-write-up/surface-write-up.tex
some 1pt additions

In particular, if $j \geq i + 2$ then $F_i^{\vec{v}} F_j^{\vec{w}}$
has a decomposition of this form for some $h_{i, j}$. We also have
that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
$\bz_{\geq 0}$-span of $(d_{h_{i, j}}, c_{h_{i, j}})$ and
$(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. The demonstration that
$h_{i, j} \neq i$ is equivalent to the proof given by O'Dorney
\cite[Theorem 6]{dorney:canonical}.

>>>>

In particular, if $j \geq i + 2$ then $F_i^{\vec{v}} F_j^{\vec{w}}$
has a decomposition of this form for some $h_{i, j}$. We also have
that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
$\bz_{\geq 0}$-span of $(d_{h_{i, j}}, c_{h_{i, j}})$ and
$(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. Furthermore, we have that
$h_{i, j} \neq i$ is equivalent to the proof given by O'Dorney
\cite[Theorem 6]{dorney:canonical}. This gives the relations
$G_{i, j}^{\vec{v}, \vec{w}}$.

The application of $G_{i, j}^{\vec{v}, \vec{w}}$ can be used
to transform any monomial in the $F_i^{\vec{v}}$'s involving
indices that differ by more than $1$ to a monomial in the $F_i
^{\vec{v}}$'s involving indices that differ by at most $1$.

Furthermore, we have relations
